\documentclass[10pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\usepackage[top=.3in, bottom=.5in, left=1in, right=1in]{geometry}
\usepackage{tgpagella}
\ifxetex
  \setmainfont[Mapping=tex-text]{Gentium}
  \setromanfont[BoldFont={Gentium Basic Bold}]{Gentium}
  \setsansfont{FontinSans-Bold}
\fi

% http://tex.stackexchange.com/questions/91124/itemize-removing-natural-indent
% http://tex.stackexchange.com/questions/78167/indentation-within-an-itemized-list
% http://tex.stackexchange.com/questions/126221/spacing-between-item-and-description-using-description-list
% http://stackoverflow.com/questions/1061112/eliminate-space-before-beginitemize
% http://tex.stackexchange.com/questions/149187/description-environment-with-italic-non-bold-labels-bullets-and-normal-font-in
\usepackage{enumitem}
\setlist{nolistsep}
\setlist[itemize]{leftmargin=.5in}
\setlist[description]{leftmargin=.5in,font=\normalfont\itshape,labelwidth=.8in,labelindent=-.5in}


\usepackage{titlesec}
\titleformat{\section}{\huge\bfseries}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{0pt}{.5em}
\titleformat{\subsection}{\large\bfseries\MakeUppercase}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\large\bfseries}{\thesubsubsection}{1em}{}

% http://tex.stackexchange.com/questions/108684/spacing-before-and-after-section-titles
\titlespacing*{\subsection}{0pt}{0pt}{0pt}
\titlespacing*{\subsubsection}{0pt}{0pt}{0pt}

\usepackage{multicol}
\pagestyle{empty}
\hyphenation{Media-Wiki}

\renewcommand{\labelitemi}{\raise .5ex\hbox{\tiny$\blacktriangleright$}}
\renewcommand{\labelitemii}{\raise .5ex\hbox{\tiny$\blacktriangleright$}}

% from http://tex.stackexchange.com/a/29796/16139
\newsavebox{\zerobox}
\newenvironment{nospace}
  {\par\edef\theprevdepth{\the\prevdepth}\nointerlineskip
   \setbox\zerobox=\vtop to 0pt\bgroup
   \hrule height0pt\kern\dimexpr\baselineskip-\topskip\relax
  }
  {\par\vss\egroup\ht\zerobox=0pt \wd\zerobox=0pt \dp\zerobox=0pt
   \box\zerobox}

\usepackage[singlespacing]{setspace}

\def\tightlist{}

\begin{document}

\begin{nospace}\begin{flushright}
Email: \href{mailto:ruben@rubenhm.org}{ruben@rubenhm.org}

Website: \href{http://www.rubenhm.org}{rubenhm.org}

314-827-6381 (c)

Citizenship: US


\end{flushright}\end{nospace}

\hypertarget{rubuxe9n-hernuxe1ndez-murillo}{%
\section{Rubén Hernández-Murillo}\label{rubuxe9n-hernuxe1ndez-murillo}}

Formats:
\href{https://raw.github.com/rubenhm/rubenhm.github.io/source/assets/docs/Ruben_Hernandez-Murillo-Resume.md}{Markdown},
\href{http://www.rubenhm.org/assets/docs/Ruben_Hernandez-Murillo-Resume.pdf}{PDF},
\href{https://raw.github.com/rubenhm/rubenhm.github.io/source/assets/docs/Ruben_Hernandez-Murillo-Resume.tex}{\LaTeX},
\href{https://raw.github.com/rubenhm/rubenhm.github.io/source/assets/docs/Ruben_Hernandez-Murillo-Resume.html}{HTML}
.

\hypertarget{work-experience}{%
\subsection{Work Experience}\label{work-experience}}

\hypertarget{research}{%
\subsubsection{Research}\label{research}}

\begin{description}
\tightlist
\item[2015-Present]
\emph{Federal Reserve Bank of Cleveland.} Senior policy economist.
\item[2005-2015]
\emph{Federal Reserve Bank of St.~Louis.} Senior economist.
\item[2000-2005]
\emph{Federal Reserve Bank of St.~Louis.} Economist.
\end{description}

\begin{itemize}
\tightlist
\item
  Published 25 scholarly articles and 40+ non-technical articles.
\item
  Served as reviewer for 30+ academic journals.
\item
  Interests: applied microeconomics, public economics, regional and
  urban, and real estate economics.
\end{itemize}

\hypertarget{policyanalysis}{%
\subsubsection{Policy/Analysis}\label{policyanalysis}}

\begin{description}
\tightlist
\item[2015-Present]
\emph{Federal Reserve Bank of Cleveland.}
\end{description}

\begin{itemize}
\tightlist
\item
  Briefed the Bank's President, Boards of Directors of the Bank's
  branches, and industry and community leaders on current economic
  conditions in the Fourth District and the nation.
\end{itemize}

\begin{description}
\tightlist
\item[2000-2015]
\emph{Federal Reserve Bank of St.~Louis.}
\end{description}

\begin{itemize}
\tightlist
\item
  Served as reviewer in Federal Reserve System's \emph{Comprehensive
  Capital Analysis and Review} (CCAR). (2012-2014)
\item
  Chaired Federal Reserve System's \emph{Committee on Regional
  Analysis}; organized its \emph{Annual Conference}. (2013-2014)
\item
  Coordinated the St.~Louis District's \emph{Beige Book}. (2002-2014)
\item
  Briefed the Bank's President, Boards of Directors of the Bank's
  branches, and industry and community leaders on current economic
  conditions in the Eighth District and the nation.
\end{itemize}

\begin{description}
\tightlist
\item[1994-1995]
\emph{ITAM, CAIE (Center for Economic Research and Analysis).} Junior
researcher.
\end{description}

\begin{itemize}
\tightlist
\item
  Wrote periodical reports on economic conditions in Mexico.
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{description}
\tightlist
\item[2001]
PhD in Economics. \emph{University of Rochester.}
\end{description}

\begin{itemize}
\tightlist
\item
  Fields: Industrial organization; political economy.\\
  Advisor: Per Krusell. Dissertation: \emph{Essays on Economic
  Competition Among Jurisdictions.}
\end{itemize}

\begin{description}
\tightlist
\item[1998]
MA in Economics. \emph{University of Rochester.}
\item[1995]
BA in Economics, \emph{summa cum laude}. \emph{ITAM (Instituto
Tecnológico Autónomo de México).}
\end{description}

\hypertarget{teaching}{%
\subsubsection{Teaching}\label{teaching}}

\begin{description}
\tightlist
\item[2013 (summer)]
\emph{Washington University in St.~Louis. Olin Business School.}
Managerial economics.
\item[2002 (spring)]
\emph{ITAM. CIE (Center for Economic Research).} Intermediate
microeconomics; industrial organization (master's).
\item[1998, 1999]
\emph{University of Rochester. Department of Economics.} Intermediate
microeconomics.
\item[1994]
\emph{ITAM. Department of Economics.} Introductory microeconomics.
\end{description}

\hypertarget{selected-publications}{%
\subsection{Selected publications}\label{selected-publications}}

\begin{description}
\tightlist
\item[2019]
\href{https://doi.org/10.1016/j.jpubeco.2019.01.012}{``Interjurisdictional
Competition with Adverse Selection.''} \emph{Journal of Public
Economics}, 173, pp.~85--95.
\item[2018]
\href{https://doi.org/10.1016/j.regsciurbeco.2017.11.005}{``A State
Level Analysis of Okun's Law.''} (with Amy Y. Guisinger, Michael T.
Owyang, and Tara Sinclair) \emph{Regional Science and Urban Economics},
68, pp.~239-248.
\item[2010]
\href{http://dx.doi.org/10.1016/j.jbankfin.2010.03.011}{``Strategic
Online Banking Adoption,''} (with Gerard Llobet and Roberto Fuentes)
\emph{Journal of Banking and Finance}, 34(7), pp.~1650--1663.
\item[2006]
\href{http://dx.doi.org/10.1016/j.ijindorg.2005.03.008}{``Patent
Licensing Revisited: Heterogeneous Firms and Product Differentiation,''}
(with Gerard Llobet). \emph{International Journal of Industrial
Organization}, 24(1), pp.~149--175.
\item[2004]
\href{http://dx.doi.org/10.1111/j.0020-6598.2004.00293.x}{``Racial
Profiling or Racist Policing? Bounds Tests in Aggregate Data,''} (with
John Knowles). \emph{International Economic Review}, 45(3),
pp.~959--989.
\end{description}

\hypertarget{hobbies}{%
\subsection{Hobbies}\label{hobbies}}

\begin{itemize}
\tightlist
\item
  \href{https://en.wikipedia.org/wiki/Scandinavian_noir}{Scandinavian
  crime fiction.}
\item
  \href{https://github.com/CapnBry/HeaterMeter/wiki}{Barbecuing with the
  Raspberry Pi.}
\item
  \href{https://www.toastmasters.org/}{Toastmasters.}
\end{itemize}

\end{document}
